#Reproducible Research - Peer Assessment 1
========================================================

## Loading and preprocessing the data

Load the data
```{r}
rawdata <- data.frame(read.csv("activity.csv"))
head(rawdata)
```

Tidy data to exclude *NA*
```{r}
cleandata <- na.omit(rawdata)
head(cleandata)
```




## What is mean total number of steps taken per day?

Grouping the total number of *steps* by *date* and plot the graphic.
```{r}
sumstep <- aggregate(cleandata$steps, list(date=cleandata$date), FUN=sum)
head(sumstep)
plot(sumstep$date, sumstep$x, type ="l")
```

Calculate and report the **mean** total number of steps taken per day
```{r}
mean1 <- aggregate(cleandata$steps, list(date=cleandata$date), mean)
head(mean1)
```

Calculate and report the **median** total number of steps taken per day
```{r}
median1 <- aggregate(cleandata$steps, list(date=cleandata$date), median)
head(median1)
```




## What is the average daily activity pattern?

Make a plot
```{r}
plot(cleandata$interval, cleandata$steps, type="l")
```

Calculate the interval base on the max of step
```{r}
approx(x=cleandata$steps, y=cleandata$interval, xout=max(cleandata$steps))
```




## Imputing missing values

### Calculate the number of **NA**
```{r}
s <- sum(is.na(rawdata))
```
The number of missing data is `r s`

### Strategy for filling in missing values  
Because the number of zero step is big (11014/17568) and the histogram is right skew so we cannot use the mean to fill in the blank. Instead we will use the **median** for the **NAs**.

### Create a new dataset
We can see that the **median** are all **0** then we can replace them all with **0**
```{r}
rawdata$steps[is.na(rawdata$steps)] <- 0
tidydata <- rawdata
head(tidydata)
```

### Make histogram, mean and median
Like doing in the 2nd part, but replace **cleandata** with **tidydata**  
Grouping the total number of *steps* by *date* and plot the graphic.
```{r}
sumstep <- aggregate(tidydata$steps, list(date=tidydata$date), FUN=sum)
head(sumstep)
plot(sumstep$date, sumstep$x, type ="l")
```

Calculate and report the **mean** total number of steps taken per day
```{r}
mean2 <- aggregate(tidydata$steps, list(date=tidydata$date), mean)
head(mean2)
```

Calculate and report the **median** total number of steps taken per day
```{r}
median2 <- aggregate(tidydata$steps, list(date=tidydata$date), median)
head(median2)
```

We can see that there is **NO** impact because the histogram is very right skew so when we added 0 to the dataset, mean and median is not changed.




## Are there differences in activity patterns between weekdays and weekends?

### Create a new factor variable in the dataset with two levels - "weekday" and "weekend" indicating whether a given date is a weekday or weekend day.
```{r}
library(openair)
tidydata$weektime <- as.factor(ifelse(weekdays(as.Date(tidydata$date)) %in% c("Saturday","Sunday"),"weekend", "weekday"))
head(tidydata)
```

